---
title: "Multigroup Confirmatory Factor Analysis"
tutorial:
  id: "mgcfa"
output: learnr::tutorial
runtime: shiny_prerendered
description: In this tutorial, you will practice a multigroup confirmatory factor analysis exploring the differences in structure and loadings for groups in a CFA.  
---

```{r setup, include=FALSE}
library(learnr)
library(learnSEM)
knitr::opts_chunk$set(echo = FALSE)
library(lavaan)
library(semPlot)
data(resdata)
library(knitr)
```

## Multigroup Confirmatory Factor Analysis

Multigroup confirmatory factor analysis (MGCFA) is a useful tool for examining the fit and structure of latent variable models across groups. You will learn how to test if groups show the same configuration, loadings, intercepts, and residuals. With this information, we can begin to think about how groups may show different results on a measure because of the qualities of the measurement, rather than experimental manipulation. You will learn the following outcomes: 

- Learn the new terminology associated with multigroup models.
- Calculate the steps to a multigroup model and assess for changes in model fit.
- Discuss the implications of complete and partial invariance for multigroup models.
- Learn how to examine latent means for overall group differences.

## MGCFA Videos

You can use `vignette("lecture_mgcfa", "learnSEM")` to view these notes in R.

<iframe width="560" height="315" src="https://www.youtube.com/embed/Kt2lZxcAGWs" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

## MGCFA Data

What is in the dataset? The Openness to Experience dataset includes the following:

**Instructions**: Below are some phrases describing people's behaviors. Please use the rating scale below to describe how accurately each statement describes you. Describe yourself as you generally are now, not as you wish to be in the future. Describe yourself as you honestly see yourself in relation to other people of your gender and of roughly your same age.  Please read each statement carefully, and then check the box that corresponds to your response.

**Scale**: very inaccurate, moderately inaccurate, neither inaccurate nor accurate, moderately accurate, very accurate

**Items**:

1.	Believe in the importance of art.
2.	Have a vivid imagination.
3.	Tend to vote for liberal political candidates.
4.	Carry the conversation to a higher level.
5.	Enjoy hearing new ideas.
6.	Enjoy thinking about things.
7.	Can say things beautifully.
8.	Enjoy wild flights of fantasy.
9.	Get excited by new ideas.
10.	Have a rich vocabulary.
11.	Am not interested in abstract ideas.
12.	Do not like art.
13.	Avoid philosophical discussions.
14.	Do not enjoy going to art museums.
15.	Tend to vote for conservative political candidates.
16.	Do not like poetry.
17.	Rarely look for a deeper meaning in things.
18.	Believe that too much tax money goes to support artists.
19.	Am not interested in theoretical discussions.
20.	Have difficulty understanding abstract ideas.

## Exercises

In this next section, you will answer questions using the *R* code blocks provided. Be sure to use the `solution` option to see the answer if you need it!

Please enter your name for submission. If you do not need to submit, just type anything you'd like in this box. 

```{r details}
question_text(
  "Student Name:",
  answer("Your Name", correct = TRUE),
  incorrect = "Thanks!",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## Data Cleanup

Using the same RS14 dataset from class, examine the multigroup analysis using `Ethnicity` as the grouping variable of interest. In this example, code 1 as Black and 2 as White. Be sure to first change the variable to a factor with labels. 

```{r cleanup, exercise = TRUE}

```

```{r cleanup-solution}
resdata$Ethnicity <- factor(resdata$Ethnicity,
                            levels = c(1,2),
                            labels = c("Black", "White"))
```

## Overall CFA

In this section, build the overall one-factor CFA for the RS14. You can use the example we did in class to get started. Include the `cfa()` and `summary()` of your model here. You should call this model `overall.model` and the latent variable should be labeled `RS`. 

```{r onefactor-setup}
resdata$Ethnicity <- factor(resdata$Ethnicity,
                            levels = c(1,2),
                            labels = c("Black", "White"))
```

```{r onefactor, exercise = TRUE}

```

```{r onefactor-solution}
overall.model <- "
RS =~ RS1 + RS2 + RS3 + RS4 + RS5 + RS6 + RS7 + RS8 + RS9 + RS10 + RS11 + RS12 + RS13 + RS14
"

overall.fit <- cfa(model = overall.model,
                   data = resdata,
                   meanstructure = TRUE)

summary(overall.fit, 
        rsquare = T, 
        standardized = T,
        fit.measures = T)
```

## White Overall Summary

Create a `white.fit` of the model for only White participants. Include the `summary()` of this model. Note that all missing data has been excluded for the rest of the analysis. 

```{r white-setup}
resdata$Ethnicity <- factor(resdata$Ethnicity,
                            levels = c(1,2),
                            labels = c("Black", "White"))
resdata <- na.omit(resdata)

overall.model <- "
RS =~ RS1 + RS2 + RS3 + RS4 + RS5 + RS6 + RS7 + RS8 + RS9 + RS10 + RS11 + RS12 + RS13 + RS14
"

overall.fit <- cfa(model = overall.model,
                   data = resdata,
                   meanstructure = TRUE)
```

```{r white, exercise = TRUE}

```

```{r white-solution}
#lots of ways to subset here's one
white.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "White", ],
                 meanstructure = TRUE)

summary(white.fit, 
        rsquare = T, 
        standardized = T,
        fit.measures = T)
```

## Black Overall Summary

Create a `black.fit` of the model for only Black participants. Include the `summary()` of this model. 

```{r black-setup}
resdata$Ethnicity <- factor(resdata$Ethnicity,
                            levels = c(1,2),
                            labels = c("Black", "White"))
resdata <- na.omit(resdata)

overall.model <- "
RS =~ RS1 + RS2 + RS3 + RS4 + RS5 + RS6 + RS7 + RS8 + RS9 + RS10 + RS11 + RS12 + RS13 + RS14
"

overall.fit <- cfa(model = overall.model,
                   data = resdata,
                   meanstructure = TRUE)

white.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "White", ],
                 meanstructure = TRUE)
```

```{r black, exercise = TRUE}

```

```{r black-solution}
#lots of ways to subset here's one
black.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "Black", ],
                 meanstructure = TRUE)

summary(black.fit, 
        rsquare = T, 
        standardized = T,
        fit.measures = T)
```

## Add the fit to table

In the code below, we've started a table for our fit indices. Fill in the section labeled `#update here` with the same `round(fitmeasures(...))` code used in the first row. 

```{r table1-setup}
resdata$Ethnicity <- factor(resdata$Ethnicity,
                            levels = c(1,2),
                            labels = c("Black", "White"))
resdata <- na.omit(resdata)

overall.model <- "
RS =~ RS1 + RS2 + RS3 + RS4 + RS5 + RS6 + RS7 + RS8 + RS9 + RS10 + RS11 + RS12 + RS13 + RS14
"

overall.fit <- cfa(model = overall.model,
                   data = resdata,
                   meanstructure = TRUE)

white.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "White", ],
                 meanstructure = TRUE)

black.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "Black", ],
                 meanstructure = TRUE)
```

```{r table1, exercise = TRUE}
table_fit <- matrix(NA, nrow = 8, ncol = 6)
colnames(table_fit) = c("Model", "X2", "df", "CFI", "RMSEA", "SRMR")
table_fit[1, ] <- c("Overall Model", round(fitmeasures(overall.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[2, ] <- c("White Model", #update here
                    )

table_fit[3, ] <- c("Black Model", #update here
                    )

kable(table_fit)
```

```{r table1-solution}
table_fit <- matrix(NA, nrow = 8, ncol = 6)
colnames(table_fit) = c("Model", "X2", "df", "CFI", "RMSEA", "SRMR")
table_fit[1, ] <- c("Overall Model", round(fitmeasures(overall.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[2, ] <- c("White Model", round(fitmeasures(white.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[3, ] <- c("Black Model", round(fitmeasures(black.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

```{r fitgroups-open}
question_text(
  "Does your model appear to fit ok overall and within each individual group?",
  answer("Both models appear to fit ok.", correct = TRUE),
  incorrect = "Both models appear to fit ok.",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## Configural Invariance

Create a `configural.fit` model using `Ethnicity` as your group variable. Include a `summary()` of this model. Add in the `configural.fit` to your table. 

```{r configural-setup}
resdata$Ethnicity <- factor(resdata$Ethnicity,
                            levels = c(1,2),
                            labels = c("Black", "White"))
resdata <- na.omit(resdata)

overall.model <- "
RS =~ RS1 + RS2 + RS3 + RS4 + RS5 + RS6 + RS7 + RS8 + RS9 + RS10 + RS11 + RS12 + RS13 + RS14
"

#models
overall.fit <- cfa(model = overall.model,
                   data = resdata,
                   meanstructure = TRUE)

white.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "White", ],
                 meanstructure = TRUE)

black.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "Black", ],
                 meanstructure = TRUE)

#kable
table_fit <- matrix(NA, nrow = 8, ncol = 6)
colnames(table_fit) = c("Model", "X2", "df", "CFI", "RMSEA", "SRMR")
table_fit[1, ] <- c("Overall Model", round(fitmeasures(overall.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[2, ] <- c("White Model", round(fitmeasures(white.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[3, ] <- c("Black Model", round(fitmeasures(black.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))
```

```{r configural, exercise = TRUE}
#put in the cfa

#put in the summary

#add to the table
table_fit[4, ] <- c("Configural Model", #update here
                    )

kable(table_fit)
```

```{r configural-solution}
#put in the cfa
configural.fit <- cfa(model = overall.model,
                      data = resdata,
                      meanstructure = TRUE,
                      group = "Ethnicity")

#put in the summary
summary(configural.fit, 
        rsquare = T, 
        standardized = T,
        fit.measures = T)

#add to the table
table_fit[4, ] <- c("Configural Model", round(fitmeasures(configural.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## Metric Invariance

In this section, create `metric.fit`, summarize the model, and add the model information to your table. 

```{r metric-setup}
resdata$Ethnicity <- factor(resdata$Ethnicity,
                            levels = c(1,2),
                            labels = c("Black", "White"))
resdata <- na.omit(resdata)

overall.model <- "
RS =~ RS1 + RS2 + RS3 + RS4 + RS5 + RS6 + RS7 + RS8 + RS9 + RS10 + RS11 + RS12 + RS13 + RS14
"

#models
overall.fit <- cfa(model = overall.model,
                   data = resdata,
                   meanstructure = TRUE)

white.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "White", ],
                 meanstructure = TRUE)

black.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "Black", ],
                 meanstructure = TRUE)

configural.fit <- cfa(model = overall.model,
                      data = resdata,
                      meanstructure = TRUE,
                      group = "Ethnicity")

#kable
table_fit <- matrix(NA, nrow = 8, ncol = 6)
colnames(table_fit) = c("Model", "X2", "df", "CFI", "RMSEA", "SRMR")
table_fit[1, ] <- c("Overall Model", round(fitmeasures(overall.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[2, ] <- c("White Model", round(fitmeasures(white.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[3, ] <- c("Black Model", round(fitmeasures(black.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[4, ] <- c("Configural Model", round(fitmeasures(configural.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))
```

```{r metric, exercise = TRUE}
#put in the cfa

#put in the summary

#add to the table
table_fit[5, ] <- c("Metric Model", #update here
                    )

kable(table_fit)
```

```{r metric-solution}
#put in the cfa
metric.fit <- cfa(model = overall.model,
                  data = resdata,
                  meanstructure = TRUE,
                  group = "Ethnicity",
                  group.equal = c("loadings"))

#put in the summary
summary(metric.fit, 
        rsquare = T, 
        standardized = T,
        fit.measures = T)

#add to the table
table_fit[5, ] <- c("Metric Model", round(fitmeasures(metric.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## Scalar Invariance

In this section, create `scalar.fit`, summarize the model, and add the model information to your table.  

```{r scalar-setup}
resdata$Ethnicity <- factor(resdata$Ethnicity,
                            levels = c(1,2),
                            labels = c("Black", "White"))
resdata <- na.omit(resdata)

overall.model <- "
RS =~ RS1 + RS2 + RS3 + RS4 + RS5 + RS6 + RS7 + RS8 + RS9 + RS10 + RS11 + RS12 + RS13 + RS14
"

#models
overall.fit <- cfa(model = overall.model,
                   data = resdata,
                   meanstructure = TRUE)

white.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "White", ],
                 meanstructure = TRUE)

black.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "Black", ],
                 meanstructure = TRUE)

configural.fit <- cfa(model = overall.model,
                      data = resdata,
                      meanstructure = TRUE,
                      group = "Ethnicity")

metric.fit <- cfa(model = overall.model,
                  data = resdata,
                  meanstructure = TRUE,
                  group = "Ethnicity",
                  group.equal = c("loadings"))

#kable
table_fit <- matrix(NA, nrow = 8, ncol = 6)
colnames(table_fit) = c("Model", "X2", "df", "CFI", "RMSEA", "SRMR")
table_fit[1, ] <- c("Overall Model", round(fitmeasures(overall.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[2, ] <- c("White Model", round(fitmeasures(white.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[3, ] <- c("Black Model", round(fitmeasures(black.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[4, ] <- c("Configural Model", round(fitmeasures(configural.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[5, ] <- c("Metric Model", round(fitmeasures(metric.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))
```

```{r scalar, exercise = TRUE}
#put in the cfa

#put in the summary

#add to the table
table_fit[6, ] <- c("Scalar Model", #update here
                    )

kable(table_fit)
```

```{r scalar-solution}
#put in the cfa
scalar.fit <- cfa(model = overall.model,
                  data = resdata,
                  meanstructure = TRUE,
                  group = "Ethnicity",
                  group.equal = c("loadings", "intercepts"))

#put in the summary
summary(metric.fit, 
        rsquare = T, 
        standardized = T,
        fit.measures = T)

#add to the table
table_fit[6, ] <- c("Scalar Model", round(fitmeasures(scalar.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## Strict (Error) Invariance

Last, add `strict.fit` by including error variances in your multigroup model, summarize that model, and include the fit information in the table. 

```{r strict-setup}
resdata$Ethnicity <- factor(resdata$Ethnicity,
                            levels = c(1,2),
                            labels = c("Black", "White"))
resdata <- na.omit(resdata)

overall.model <- "
RS =~ RS1 + RS2 + RS3 + RS4 + RS5 + RS6 + RS7 + RS8 + RS9 + RS10 + RS11 + RS12 + RS13 + RS14
"

#models
overall.fit <- cfa(model = overall.model,
                   data = resdata,
                   meanstructure = TRUE)

white.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "White", ],
                 meanstructure = TRUE)

black.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "Black", ],
                 meanstructure = TRUE)

configural.fit <- cfa(model = overall.model,
                      data = resdata,
                      meanstructure = TRUE,
                      group = "Ethnicity")

metric.fit <- cfa(model = overall.model,
                  data = resdata,
                  meanstructure = TRUE,
                  group = "Ethnicity",
                  group.equal = c("loadings"))

scalar.fit <- cfa(model = overall.model,
                  data = resdata,
                  meanstructure = TRUE,
                  group = "Ethnicity",
                  group.equal = c("loadings", "intercepts"))

#kable
table_fit <- matrix(NA, nrow = 8, ncol = 6)
colnames(table_fit) = c("Model", "X2", "df", "CFI", "RMSEA", "SRMR")
table_fit[1, ] <- c("Overall Model", round(fitmeasures(overall.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[2, ] <- c("White Model", round(fitmeasures(white.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[3, ] <- c("Black Model", round(fitmeasures(black.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[4, ] <- c("Configural Model", round(fitmeasures(configural.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[5, ] <- c("Metric Model", round(fitmeasures(metric.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[6, ] <- c("Scalar Model", round(fitmeasures(scalar.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))
```

```{r strict, exercise = TRUE}
#put in the cfa

#put in the summary

#add to the table
table_fit[7, ] <- c("Strict Model", #update here
                    )

kable(table_fit)
```

```{r strict-solution}
#put in the cfa
strict.fit <- cfa(model = overall.model,
                  data = resdata,
                  meanstructure = TRUE,
                  group = "Ethnicity",
                  group.equal = c("loadings", "intercepts", "residuals"))

#put in the summary
summary(strict.fit, 
        rsquare = T, 
        standardized = T,
        fit.measures = T)

#add to the table
table_fit[7, ] <- c("Strict Model", round(fitmeasures(strict.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

```{r scalar-open}
question_text(
  "Looking at your results, do you see anywhere that indicates non-invariance (i.e., has a larger change than CFI = .01)? Where did it appear to break down?",
  answer("At the strict step!", correct = TRUE),
  incorrect = "The model stops being invariant at the strict step.",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## Partial Invariance

Use the code provided from class to calculate the potential pathway that should be freed to improve our model fit for partial invariance. The code has been partially provided for you. Fill in the sections labeled `#fill in here` with the appropriate code. For the `partial_synatx` you should fill in the `lavaan` syntax for the step that broken down (i.e., `=~` for loadings, `~1` for intercepts, or `~~` for residuals). In the model section, fill in `group.equal` with the appropriate step for where your model broken down. 

```{r partial-setup}
resdata$Ethnicity <- factor(resdata$Ethnicity,
                            levels = c(1,2),
                            labels = c("Black", "White"))
resdata <- na.omit(resdata)

overall.model <- "
RS =~ RS1 + RS2 + RS3 + RS4 + RS5 + RS6 + RS7 + RS8 + RS9 + RS10 + RS11 + RS12 + RS13 + RS14
"

#models
overall.fit <- cfa(model = overall.model,
                   data = resdata,
                   meanstructure = TRUE)

white.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "White", ],
                 meanstructure = TRUE)

black.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "Black", ],
                 meanstructure = TRUE)

configural.fit <- cfa(model = overall.model,
                      data = resdata,
                      meanstructure = TRUE,
                      group = "Ethnicity")

metric.fit <- cfa(model = overall.model,
                  data = resdata,
                  meanstructure = TRUE,
                  group = "Ethnicity",
                  group.equal = c("loadings"))

scalar.fit <- cfa(model = overall.model,
                  data = resdata,
                  meanstructure = TRUE,
                  group = "Ethnicity",
                  group.equal = c("loadings", "intercepts"))

strict.fit <- cfa(model = overall.model,
                  data = resdata,
                  meanstructure = TRUE,
                  group = "Ethnicity",
                  group.equal = c("loadings", "intercepts", "residuals"))

#kable
table_fit <- matrix(NA, nrow = 8, ncol = 6)
colnames(table_fit) = c("Model", "X2", "df", "CFI", "RMSEA", "SRMR")
table_fit[1, ] <- c("Overall Model", round(fitmeasures(overall.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[2, ] <- c("White Model", round(fitmeasures(white.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[3, ] <- c("Black Model", round(fitmeasures(black.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[4, ] <- c("Configural Model", round(fitmeasures(configural.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[5, ] <- c("Metric Model", round(fitmeasures(metric.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[6, ] <- c("Scalar Model", round(fitmeasures(scalar.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[7, ] <- c("Strict Model", round(fitmeasures(strict.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))
```

```{r partial, exercise = TRUE}
##write out partial codes
partial_syntax <- paste(colnames(res.data)[3:16], #all the columns
                        ##fill in here
                        colnames(res.data)[3:16]) #all columns again 
partial_syntax

CFI_list  <- 1:length(partial_syntax)
names(CFI_list) <- partial_syntax

for (i in 1:length(partial_syntax)){
  
  temp <- cfa(model = overall.model, 
              data = resdata,
              meanstructure = TRUE,
              group = "Ethnicity",
              group.equal = #fill in here,
              group.partial = partial_syntax[i])
  
  CFI_list[i] <- fitmeasures(temp, "cfi")
}

which.max(CFI_list)
```

```{r partial-solution}
##write out partial codes
partial_syntax <- paste(colnames(resdata)[3:16], #all the columns
                        "~~",
                        colnames(resdata)[3:16]) #all columns again 
partial_syntax

CFI_list  <- 1:length(partial_syntax)
names(CFI_list) <- partial_syntax

for (i in 1:length(partial_syntax)){
  
  temp <- cfa(model = overall.model, 
              data = resdata,
              meanstructure = TRUE,
              group = "Ethnicity",
              group.equal = c("loadings", "intercepts", "residuals"),
              group.partial = partial_syntax[i])
  
  CFI_list[i] <- fitmeasures(temp, "cfi")
}

which.max(CFI_list)
```

Create `partial.fit` by updating your model to allow for the freed parameter. Summarize the model, and add this model's fit information to your table. 

```{r partial2-setup}
resdata$Ethnicity <- factor(resdata$Ethnicity,
                            levels = c(1,2),
                            labels = c("Black", "White"))
resdata <- na.omit(resdata)

overall.model <- "
RS =~ RS1 + RS2 + RS3 + RS4 + RS5 + RS6 + RS7 + RS8 + RS9 + RS10 + RS11 + RS12 + RS13 + RS14
"

#models
overall.fit <- cfa(model = overall.model,
                   data = resdata,
                   meanstructure = TRUE)

white.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "White", ],
                 meanstructure = TRUE)

black.fit <- cfa(model = overall.model,
                 data = resdata[resdata$Ethnicity == "Black", ],
                 meanstructure = TRUE)

configural.fit <- cfa(model = overall.model,
                      data = resdata,
                      meanstructure = TRUE,
                      group = "Ethnicity")

metric.fit <- cfa(model = overall.model,
                  data = resdata,
                  meanstructure = TRUE,
                  group = "Ethnicity",
                  group.equal = c("loadings"))

scalar.fit <- cfa(model = overall.model,
                  data = resdata,
                  meanstructure = TRUE,
                  group = "Ethnicity",
                  group.equal = c("loadings", "intercepts"))

strict.fit <- cfa(model = overall.model,
                  data = resdata,
                  meanstructure = TRUE,
                  group = "Ethnicity",
                  group.equal = c("loadings", "intercepts", "residuals"))

#kable
table_fit <- matrix(NA, nrow = 8, ncol = 6)
colnames(table_fit) = c("Model", "X2", "df", "CFI", "RMSEA", "SRMR")
table_fit[1, ] <- c("Overall Model", round(fitmeasures(overall.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[2, ] <- c("White Model", round(fitmeasures(white.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[3, ] <- c("Black Model", round(fitmeasures(black.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[4, ] <- c("Configural Model", round(fitmeasures(configural.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[5, ] <- c("Metric Model", round(fitmeasures(metric.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[6, ] <- c("Scalar Model", round(fitmeasures(scalar.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[7, ] <- c("Strict Model", round(fitmeasures(strict.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))
```

```{r partial2, exercise = TRUE}
#put in the cfa

#put in the summary

#add to the table
table_fit[8, ] <- c("Partial Model", #update here
                    )

kable(table_fit)
```

```{r partial2-solution}
#put in the cfa
partial.fit <- cfa(model = overall.model,
                   data = resdata,
                   meanstructure = TRUE,
                   group = "Ethnicity",
                   group.equal = c("loadings", "intercepts", "residuals"),
                   group.partial = c("RS3 ~~ RS3"))

#put in the summary
summary(partial.fit, 
        rsquare = T, 
        standardized = T,
        fit.measures = T)

#add to the table
table_fit[8, ] <- c("Partial Model", round(fitmeasures(partial.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

```{r freeparameter-open}
question_text(
  "Does the freeing of this one parameter bring your model up to partial invariance for that step?",
  answer("No not quite. We could run this again and check for another parameter.", correct = TRUE),
  incorrect = "No not quite. We could run this again and check for another parameter.",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

```{r partialinterpret-open}
question_text(
  "What does the result of the partial invariance step imply for interpreting this scale? ",
  answer("Blacks and Whites have different variances for RS3.", correct = TRUE),
  incorrect = "Blacks and Whites have different variances for RS3 (and maybe one more), otherwise, the scale is invariant.",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## Submit

On this page, you will create the submission for your instructor (if necessary). Please copy this report and submit using a Word document or paste into the text window of your submission page. Click "Generate Submission" to get your work! 

```{r context="server"}
encoder_logic()
```

```{r encode, echo=FALSE}
encoder_ui()
```

