---
title: "Item Response Theory"
tutorial:
  id: "irt"
output: learnr::tutorial
runtime: shiny_prerendered
description: In this tutorial, you will practice running item response theory on dichotomous and polytomous data types. 
---

```{r setup, include=FALSE}
library(learnr)
library(learnSEM)
knitr::opts_chunk$set(echo = FALSE)
library(mirt)
library(ltm)
data(dirtdata)
data(mirtdata)
mirtdata$q5 <- 8 - mirtdata$q5
mirtdata$q8 <- 8 - mirtdata$q8
mirtdata$q13 <- 8 - mirtdata$q13
```

## Item Response Theory

Item Response Theory is a latent trait analysis with a different focus traditionally used in understanding how a test performs. We will examine both dichotomous (yes/no) and polytomous (multiple options) scales to determine each item's characteristics. The learning outcomes are:

- Compare item response theory to classical test theory.
- Understand the usage and differences of an IRT model to a CFA model.
- Estimate 2 and 3 parameter logistic models on dichotomous data.
- Estimate a graded partial credit model for polytomous data.

## IRT Videos

You can use `vignette("lecture_irt", "learnSEM")` to view these notes in R.

<iframe width="560" height="315" src="https://www.youtube.com/embed/vpP52NnandU " frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>


## Exercises

In this next section, you will answer questions using the *R* code blocks provided. Be sure to use the `solution` option to see the answer if you need it!

Please enter your name for submission. If you do not need to submit, just type anything you'd like in this box. 

```{r details}
question_text(
  "Student Name:",
  answer("Your Name", correct = TRUE),
  incorrect = "Thanks!",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## Dichotomous IRT

The included dataset includes data from an Educational Psychology Test scored as 0 (answered incorrectly) and 1 (answered correctly). The data has been imported for you. 

```{r echo = T}
data(dirtdata)
head(dirtdata)
```

## Two Parameter Logistic

Include a 2PL calculated on just columns V2 through V5. Save the model as `edu.model`. Use the `coef()` function to examine the difficulty and discrimination parameters. 

```{r twopl, exercise = TRUE}

```

```{r twopl-solution}
edu.model <- ltm(dirtdata ~ z1, IRT.param = TRUE)
coef(edu.model)
```

## 2PL Plots

Include the ICC and TIF plots to view all the items and overall test information at once. 
```{r twoplplot-setup}
edu.model <- ltm(dirtdata ~ z1, IRT.param = TRUE)
```

```{r twoplplot, exercise = TRUE}

```

```{r twoplplot-solution}
plot(edu.model, type = "IIC")
plot(edu.model, type = "IIC", items = 0)
```

## Three Parameter Logistic

Include the 3PL model as `edu2.model`. Use the `coef()` function to examine the difficulty, discrimination, and guessing parameters. Name this model `edu.model2`. 

```{r threepl, exercise = TRUE}

```

```{r threepl-solution}
edu.model2 <- tpm(dirtdata, type="latent.trait", IRT.param = TRUE)
coef(edu.model2)
```

## 3PL Plots

Include the ICC and TIF plots to view all the items and overall test information at once.

```{r threeplplot-setup}
edu.model2 <- tpm(dirtdata, type="latent.trait", IRT.param = TRUE)
```

```{r threeplplot, exercise = TRUE}

```

```{r threeplplot-solution}
plot(edu.model2, type="ICC")
plot(edu.model2, type = "IIC", items = 0)
```

## Compare Models

Use the `anova()` function to compare the two models. 

```{r compare-setup}
edu.model <- ltm(dirtdata ~ z1, IRT.param = TRUE)
edu.model2 <- tpm(dirtdata, type="latent.trait", IRT.param = TRUE)
```

```{r compare, exercise = TRUE}

```

```{r compare-solution}
anova(edu.model, edu.model2)
```

```{r best-open}
question_text(
  "Which model was better? Does it appear that the guessing parameter adds something useful to the model? ",
  answer("Nope! The 2PL is a better representation.", correct = TRUE),
  incorrect = "Nope! The 2PL is a better representation.",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

```{r good2pl-open}
question_text(
  "Which items would be considered good items based on discrimination?",
  answer("Nearly all are good discriminators, but pretty easy.", correct = TRUE),
  incorrect = "Nearly all are good discriminators, but pretty easy.",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## Polytomous IRT 

Load the assignment_mirt data below. You should reverse code items 5, 8, and 13 using `8 - columns` to ensure all items are in the same direction. The scale included examines evaluations of job candidates rated on 15 different qualities. 

```{r echo = T}
data(mirtdata)
head(mirtdata)
```

## Graded Partial Credit Model

Create a graded partial credit model to analyze the scale, and save this model as `gpcm.model`. Include the `coef()` for the model to help you answer the questions below. 

```{r gpcm, exercise = TRUE}

```

```{r gpcm-solution}
gpcm.model <- mirt(data = mirtdata, 
                  model = 1, 
                  itemtype = "gpcm")

coef(gpcm.model, IRTpars = T)
```

## GPCM Plots

Include the ICC and TIF plots to view all the items and overall test information at once.

```{r gpcmplots-setup}
gpcm.model <- mirt(data = mirtdata, 
                  model = 1, 
                  itemtype = "gpcm")
```

```{r gpcmplots, exercise = TRUE}

```

```{r gpcmplots-solution}
plot(gpcm.model, type = "trace") 
plot(gpcm.model, type = "info")
```

```{r order-open}
question_text(
  "Examine the items. Do they appear ordered where each answer function is ordered correctly from 1 to 7?",
  answer("Yes, they mostly appear ordered.", correct = TRUE),
  incorrect = "Yes, they mostly appear ordered.",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

```{r allscale-open}
question_text(
  "Examine the items. Do we need all 7 items on this scale? (i.e., do they all have the probability of being the most likely answer choice?)",
  answer("Unlikely, maybe only four points.", correct = TRUE),
  incorrect = "Unlikely, maybe only four points.",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

```{r goodquestions-open}
question_text(
  "Which items indicate good discrimination?",
  answer("Pretty much all of them but 8 and 13.", correct = TRUE),
  incorrect = "Pretty much all of them but 8 and 13.",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```
        
## Submit

On this page, you will create the submission for your instructor (if necessary). Please copy this report and submit using a Word document or paste into the text window of your submission page. Click "Generate Submission" to get your work! 

```{r context="server"}
encoder_logic()
```

```{r encode, echo=FALSE}
encoder_ui()
```
