---
title: "Full SEM"
tutorial:
  id: "fullsem"
output: learnr::tutorial
runtime: shiny_prerendered
description: In this tutorial, you will learn how analyze a fully latent structural equation model. 
---

```{r setup, include=FALSE}
library(learnr)
library(learnSEM)
knitr::opts_chunk$set(echo = FALSE)
library(lavaan)
library(semPlot)
university.cov <- lav_matrix_lower2full(
    c(169.00, 
      73.710, 182.2500,
      73.229, 88.4250, 171.6100,
      63.375, 72.5625, 127.7250, 156.2500,
      42.120, 67.4325, 122.0265, 123.1875, 182.2500,
      57.226, 63.2610, 117.1926, 154.4250, 138.0240, 201.6400,
      30.875, 32.0625, 60.9805, 62.9375, 76.9500, 79.5910, 90.2500,
      36.075, 38.9610, 61.0722, 58.2750, 65.9340, 70.9290, 81.1965, 123.2100,
      18.096, 21.1410, 26.2131, 39.1500, 44.6310, 46.9452, 48.7635, 56.0106, 75.6900))

rownames(university.cov) <-
    colnames(university.cov) <-
    c("class", "social", "learn", "chronic", "physical", "sex", 
      "depression", "anxiety", "stress")
```

## Full Structural Equation Models 

This section of the course increases your skills by expanding from measurement models and CFA to full structural models. We will begin to use the latent variables to predict each other or add other covariates to predict the measurement models. You will use the `sem()` function and learn more about how to write `lavaan` code for composite variables. The learning outcomes are:

- Build, analyze, summarize, and diagram a full structural equation model
- Learn specific composite variable code
- Troubleshoot Heywood cases in these models

## Full SEM Videos

Placeholder screen for videos after they are completed. 

## Exercises

In this next section, you will answer questions using the *R* code blocks provided. Be sure to use the `solution` option to see the answer if you need it!

Please enter your name for submission. If you do not need to submit, just type anything you'd like in this box. 

```{r details}
question_text(
  "Student Name:",
  answer("Your Name", correct = TRUE),
  incorrect = "Thanks!",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## The Data

The data is provided for you below, and it has been loaded for you in the background, along with the `lavaan` and `semPlot` libraries. The data contains:

  - University composite (formative): 
      - Class - perception of the way school work, classes, grades, and other related academic goals are going for a student.
      - Social - perception of social networks, friendships, support systems, and connectedness on campus.
      - Learning - perception of student's happiness with the learning environment on campus (professors, academic support, fit with major, etc.).
  - Psychological factor (reflexive):
      - Depression
      - Anxiety
      - Stress
  - Health factor (reflexive):
      - Chronic health issues
      - Physical fitness and active health
      - Sexual health

```{r}
university.cov <- lav_matrix_lower2full(
    c(169.00, 
      73.710, 182.2500,
      73.229, 88.4250, 171.6100,
      63.375, 72.5625, 127.7250, 156.2500,
      42.120, 67.4325, 122.0265, 123.1875, 182.2500,
      57.226, 63.2610, 117.1926, 154.4250, 138.0240, 201.6400,
      30.875, 32.0625, 60.9805, 62.9375, 76.9500, 79.5910, 90.2500,
      36.075, 38.9610, 61.0722, 58.2750, 65.9340, 70.9290, 81.1965, 123.2100,
      18.096, 21.1410, 26.2131, 39.1500, 44.6310, 46.9452, 48.7635, 56.0106, 75.6900))

rownames(university.cov) <-
    colnames(university.cov) <-
    c("class", "social", "learn", "chronic", "physical", "sex", 
      "depression", "anxiety", "stress")
```

## Specify Your Model

In this section, we will specific our overall `composite.model` by creating three latent variables for our measurement model:
    
  - `University`: class, social, learn as a composite variable
  - `Health`: chronic, physical, sex as a reflexive variable
  - `Psychology`: depression, anxiety, stress as a reflexive variable
    
The structural model should include the university composite predicting both the psychological and health factors. We expect that as university perception changes, changes in mental and physical health symptoms should exist as well. Note: all variables have been scaled so that high scores are negative indicators. 

```{r model1, exercise = TRUE}

```

```{r model1-solution}
composite.model <- '
University <~ class + social + learn
Health =~ chronic + physical + sex
Psychology =~ depression + anxiety + stress
Psychology ~ University
Health ~ University
'
```

## Analyze the Model

Analyze your `composite.model` using the `sem()` function, and name the output `composite.fit`. There are 300 participants in the dataset. 

```{r analyze1-setup}
composite.model <- '
University <~ class + social + learn
Health =~ chronic + physical + sex
Psychology =~ depression + anxiety + stress
Psychology ~ University
Health ~ University
'
```

```{r analyze1, exercise = TRUE}

```

```{r analyze1-solution, warning = F, message = F}
composite.fit <- sem(model = composite.model, 
                     sample.cov = university.cov, 
                     sample.nobs = 300)
```

Oh no! Your model says it is not identified. What should you do? In this case, we have to remember that the entire model has to be identified. Let's look at a picture to see where that might be:

```{r echo = F, warning = F, messsage = F}
composite.model <- '
University <~ class + social + learn
Health =~ chronic + physical + sex
Psychology =~ depression + anxiety + stress
Psychology ~ University
Health ~ University
'

composite.fit <- sem(model = composite.model, 
                     sample.cov = university.cov, 
                     sample.nobs = 300)

semPaths(composite.fit, 
         whatLabels = "std", 
         layout = "spring",
         edge.label.cex = 1)
```

Because University is predicting only Psychology and Health, we have two regression paths that act like a small measurement model for University. The identification for this section is not met, so we need to set them equal to each other or create a marker variable to control for these paths. The easiest solution is to set `University =~ Psychology + Health` rather than set two separate regressions. Rerun your `composite.fit` to make sure you do not get an error. 

```{r example-fix, echo = TRUE}
composite.model <- '
University <~ class + social + learn
Health =~ chronic + physical + sex
Psychology =~ depression + anxiety + stress
University =~ Psychology + Health
'
```

```{r analyze2-setup}
composite.model <- '
University <~ class + social + learn
Health =~ chronic + physical + sex
Psychology =~ depression + anxiety + stress
University =~ Psychology + Health
'
```


```{r analyze2, exercise = TRUE}

```

```{r analyze2-solution}
composite.fit <- sem(model = composite.model, 
                     sample.cov = university.cov, 
                     sample.nobs = 300)
```

## Summarize Your Model

Let's summarize the final model you just created. Use the `summary()` function on both models with the standardized solution, r-square values, and fit.measures all included. 

```{r summarize1-setup}
composite.model <- '
University <~ class + social + learn
Health =~ chronic + physical + sex
Psychology =~ depression + anxiety + stress
University =~ Psychology + Health
'

composite.fit <- sem(model = composite.model, 
                     sample.cov = university.cov, 
                     sample.nobs = 300)
```

```{r summarize1, exercise = TRUE}

```

```{r summarize1-solution}
summary(composite.fit,
        standardized = TRUE,
        rsquare = TRUE,
        fit.measures = TRUE)
```

```{r parameter-open}
question_text(
  "Look at the solution of the final model and describe that model. Do all of the items load with their latent variable? Does university appear to predict psychological and health factors?",
  answer("Lots of right answers.", correct = TRUE),
  incorrect = "Be sure to detail your answer! It appears that psychological and health items load on their latent, but the university latent is not a very good composite. Additionally, the university variable does predict the other two latents but it's likely driven by the learning environment which is related to the university variable.",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## Create a Picture

Use `semPaths()` to create a picture of your full structural model. Use `std` for the `whatLabels` argument, any layout you would like, and `edge.label.cex = 1` to increase the font size.

```{r diagram1-setup}
composite.model <- '
University <~ class + social + learn
Health =~ chronic + physical + sex
Psychology =~ depression + anxiety + stress
University =~ Psychology + Health
'

composite.fit <- sem(model = composite.model, 
                     sample.cov = university.cov, 
                     sample.nobs = 300)
```

```{r diagram1, exercise = TRUE}

```

```{r diagram1-solution}
semPaths(composite.fit, 
         whatLabels = "std", 
         layout = "spring",
         edge.label.cex = 1)
```

## Submit

On this page, you will create the submission for your instructor (if necessary). Please copy this report and submit using a Word document or paste into the text window of your submission page. Click "Generate Submission" to get your work! 

```{r context="server"}
encoder_logic()
```

```{r encode, echo=FALSE}
encoder_ui()
```
